Boosted Regression Trees for Predictive Auto-Tuning

### 2011-12-13 paper/draft1.tex

Once an accurate regression model has been fit to the data, it remains to be optimized for novel arguments (Fig.~\ref{fig:autotune_general}, bottom, step 4).
An exhaustive search is the most reliable if it can be afforded, but in our experiments
(as in general) an exhaustive search is prohibitively expensive.
In our experiments we compare two strategies: (1) a hand-chosen grid provided by the authors of the kernel used in our experiments \citep{pinto+cox:2011gcg},
and (2) a generic stochastic hill-climbing search.

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiment Setup}

>>>>

Once an accurate regression model has been fit to the data, it remains to be optimized for novel arguments (Fig.~\ref{fig:autotune_general}, bottom, step 4).
An exhaustive search is the most reliable if it can be afforded, but in our experiments
(as in general) an exhaustive search is prohibitively expensive.
In our experiments we compare two strategies:
(1)
a generic stochastic hill-climbing search,
and (2)
a hand-chosen grid provided by the authors of the kernel used in our experiments \citep{pinto+cox:2011gcg}.
The {\em hill-climing} (HC) search algorithm starts from the reference
implementation and resamples each of the parameters
of the current best implementation randomly with
probability $0.25$ (keeping the current best setting with probability $0.75$).
On each hill-climbing iteration, if the speed of the newly sampled point is greater than the previous point, then it becomes the current point.
We show results for search variants HC25, HC50, and HC75, which correspond do hill-climbin for 25, 50, and 75 iterations respectively.
The {\em grid} algorithm is specific to the kernel used in our case study,
the details of the grid are provided with our experimental results in Section~\ref{sec:refgrid}

@@

\subsection{Reference and Grid}
\label{sec:refgrid}
The reference implementation XXX

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experiment Setup}
